dynamics

### 2023-03-01 scripts/workshop/dynamics.Rmd
try more dynamics

combined <- contour(trans_1_min = 0.0001,trans_1_max = 0.001,trans_3_min = 0.0001,trans_3_max = 0.001,mort1 = c(1/70),mort2 = c(1/35),degr = 1/3.895598)

@@

@@

output_x <- as.data.frame(lsoda(xstart_x,times,rm0,params_x)) # tells computer to solve (integrate) equations
output_x1 <- as.data.frame(lsoda(xstart_x,times,rm1,params_x)) # tells computer to solve (integrate) equations

combined_eigen <- combined$eigen[param_num]
```

@@

output_a1 %<>% mutate(I = Ia+Ib)
output_c1 %<>% mutate(I = Ia+Ib)
output_h1 %<>% mutate(I = Ia+Ib)
output_n1 %<>% mutate(I = Ia+Ib)
output_x1 %<>% mutate(I = Ia+Ib)
```

```{r}
color_x <- paste("Combined\nR0=", combined_eigen)
color_c <- paste("Composition\nR0=", community_eigen)
color_a <- paste("Abundance\nR0=", abundance_eigen)
color_h <- paste("Halflife\nR0=", halflife_eigen)
color_n <- paste("Reference\nR0=", reference_eigen)

@@

>>>>

combined <- contour(trans_1_min = 0.0001,trans_1_max = 0.001,trans_3_min = 0.0001,trans_3_max = 0.001,mort1 = c(1/70),mort2 = c(1/35),degr = 1/3.895598)
#abundance and half life
combined_1 <- contour(trans_1_min = 0.0001,trans_1_max = 0.001,trans_3_min = 0.0001,trans_3_max = 0.001,mort1 = c(1/45),mort2 = c(1/45),degr = 1/3.895598)
#abundance and composition
combined_2 <- contour(trans_1_min = 0.0001,trans_1_max = 0.001,trans_3_min = 0.0001,trans_3_max = 0.001,mort1 = c(1/70),mort2 = c(1/35),degr = 1/1.947799)
#composition and half life
combined_3 <- contour(trans_1_min = 0.0001,trans_1_max = 0.001,trans_3_min = 0.0001,trans_3_max = 0.001,mort1 = c(1/52.5),mort2 = c(1/52.5),degr=1/3.895598)

@@

#abundance and halflife
params_x1 <- c(mu_a=1/45,
          mu_b=1/45,
          beta=spec_1,
          betab=spec_2,
          phi=env_rate,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/3.895598)  # model parameters

#abundance and composition
params_x2 <- c(mu_a=1/52.5,
          mu_b=1/52.5,
          beta=spec_1,
          betab=spec_2,
          phi=env_rate,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/1.947799)  # model parameters

#composition and halflife
params_x3 <- c(mu_a=1/60,
          mu_b=1/30,
          beta=spec_1,
          betab=spec_2,
          phi=env_rate,
          lambda=5/3,
          alpha=1/10,
          sigma=1/2,
          epsilon=1/3.895598)  # model parameters

@@

xstart_x1 <- c(Sa=params_x1[[6]]/params_x1[[1]],
          Ia=1,
          Ra=0,
          Sb=params_x1[[6]]/params_x1[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

xstart_x2 <- c(Sa=params_x2[[6]]/params_x2[[1]],
          Ia=1,
          Ra=0,
          Sb=params_x2[[6]]/params_x2[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

xstart_x3 <- c(Sa=params_x3[[6]]/params_x3[[1]],
          Ia=1,
          Ra=0,
          Sb=params_x3[[6]]/params_x3[[2]],
          Ib=1,
          Rb=0,
          V=0)  # initial conditions

output_x <- as.data.frame(lsoda(xstart_x,times,rm0,params_x)) # tells computer to solve (integrate) equations
output_x1 <- as.data.frame(lsoda(xstart_x,times,rm1,params_x)) # tells computer to solve (integrate) equations
output_x2 <- as.data.frame(lsoda(xstart_x1,times,rm1,params_x1)) # tells computer to solve (integrate) equations
output_x3 <- as.data.frame(lsoda(xstart_x2,times,rm1,params_x2)) # tells computer to solve (integrate) equations
output_x4 <- as.data.frame(lsoda(xstart_x3,times,rm1,params_x3)) # tells computer to solve (integrate) equations

combined_eigen <- combined$eigen[param_num]
combined_eigen_1 <- combined_1$eigen[param_num]
combined_eigen_2 <- combined_2$eigen[param_num]
combined_eigen_3 <- combined_3$eigen[param_num]

@@

output_a1 %<>% mutate(I = Ia+Ib)
output_c1 %<>% mutate(I = Ia+Ib)
output_h1 %<>% mutate(I = Ia+Ib)
output_n1 %<>% mutate(I = Ia+Ib)
output_x1 %<>% mutate(I = Ia+Ib)
output_x2 %<>% mutate(I = Ia+Ib)
output_x3 %<>% mutate(I = Ia+Ib)
output_x4 %<>% mutate(I = Ia+Ib)
```

```{r}
color_x <- paste("Combined\nR0=", combined_eigen)
color_x2 <- paste("Abun_Half\nR0=", combined_eigen_1)
color_x3 <- paste("Abun_Comp\nR0=", combined_eigen_2)
color_x4 <- paste("Comp_Half\nR0=", combined_eigen_3)

color_c <- paste("Composition\nR0=", community_eigen)
color_a <- paste("Abundance\nR0=", abundance_eigen)
color_h <- paste("Halflife\nR0=", halflife_eigen)
color_n <- paste("Reference\nR0=", reference_eigen)

@@

```{r}
ggplot()+
  geom_line(data=output_x1,mapping = aes(y=I,x=time, color=color_x))+
  scale_color_manual(name="",values = "black")+
  new_scale_color()+
  geom_line(data=output_x2, mapping=aes(y=I,x=time, color=color_x2))+
  scale_color_manual(name="",values = "red")+
  new_scale_color()+
  geom_line(output_x3, mapping=aes(y=I,x=time, color=color_x3))+
  scale_color_manual(name="",values = "orange")+
  new_scale_color()+
  geom_line(output_x4, mapping=aes(y=I,x=time, color=color_x4))+
  scale_color_manual(name="",values = "purple")+
  labs(y="N",x="Time")+
  ylim(0,40)+
  ggtitle(paste("Total Infected Individuals (2 Species) Over Time Across Varying Conditions w/o demo"))+
  theme_bw()
```
